Ascension Island Implementation

### 2025-01-13 Implementation doc/Draft1.Rmd
updated files

---
title: "Ascension Island Implementation"
subtitle: "StrathE2E"
author: 
output: 
  pagedreport::paged_hazelnuts:
    logo: "https://www.r-project.org/logo/Rlogo.svg"
    img_to_dark: TRUE
    logo_to_white: TRUE
    front_img: "img/Front.png"
    back_img: "img/Back.png"
    other_css: "tweaks.css"
knit: pagedown::chrome_print
main-color: "#000000"
secondary-color: "#737372"
main-font: "Quicksand"
bibliography: "IMP.bib"
chrome_path: "C:/ProgramData/Microsoft/Windows/Start Menu/Programs/Google Chrome.lnk"
editor_options: 
  markdown: 
    wrap: sentence
---

@@

[to be completed]

>>>>

<<<<<<< HEAD
---
title: "Ascension Island Implementation"
subtitle: "StrathE2E"
author: 
output: 
  pagedreport::paged_hazelnuts:
    logo: "https://www.r-project.org/logo/Rlogo.svg"
    img_to_dark: TRUE
    logo_to_white: TRUE
    front_img: "img/Front.png"
    back_img: "img/Back.png"
    other_css: "tweaks.css"
knit: pagedown::chrome_print
main-color: "#000000"
secondary-color: "#737372"
main-font: "Quicksand"
bibliography: "IMP.bib"
chrome_path: "C:/ProgramData/Microsoft/Windows/Start Menu/Programs/Google Chrome.lnk"
editor_options: 
  markdown: 
    wrap: sentence
---

@@

[to be completed]
=======
---
title: "Ascension Island Implementation"
subtitle: "StrathE2E"
author: 
output: 
  pagedreport::paged_hazelnuts:
    logo: "https://www.r-project.org/logo/Rlogo.svg"
    img_to_dark: TRUE
    logo_to_white: TRUE
    front_img: "img/Front.png"
    back_img: "img/Back.png"
    other_css: "tweaks.css"
knit: pagedown::chrome_print
main-color: "#000000"
secondary-color: "#737372"
main-font: "Quicksand"
bibliography: "IMP.bib"
chrome_path: "C:/ProgramData/Microsoft/Windows/Start Menu/Programs/Google Chrome.lnk"
editor_options: 
  markdown: 
    wrap: sentence
---

[to be completed]
>>>>>>> dcdc94e72005e07779b9f291ff885f150aa57656
